This is my paper title

### 2023-04-05 outputs/paper/paper.qmd
Removing no longer needed graph
Correcting issues with graphs

#### Quarto workspace setup and reading csv's into quarto ####
library(tidyverse)
library(palmerpenguins)
library(haven)
library(here)
library(dplyr)

@@

clean_data_degree$degree <-
  factor(degrees_clean$degree,
         levels = c("< High School", "High School", "Junior College", "Bachelors", "Graduate"))

@@

clean_data_willingness$grnprice <-
  factor(willingness_clean$grnprice,
         levels = c("Very Unwilling", "Fairly Unwilling", "Neutral", "Fairly Willing", "Very Willing"))

@@

degree_and_willingness <-
  clean_data_degree |>
  left_join(clean_data_willingness, by = join_by(id), suffix = c("Degree", "Willingness"))

@@

#clean_data |>
#  ggplot(mapping = aes(x = degrees_clean, fill = grnmoney)) +
# geom_bar(position = "dodge2")

>>>>

#### Quarto workspace setup and reading csv's into quarto ####
library(tidyverse)
library(palmerpenguins)
library(haven)
library(here)
library(dplyr)
library(labelled)

@@

@@

@@

@@
